Introduction to Markov state modeling with the PyEMMA software [Article v\versionnumber]

### 2018-11-28 manuscript/manuscript.tex
replace text-based reference with proper label

We further assume that the reader is familiar with the basic ideas and theory underlying Markov modeling and will only give a brief reminder of the basic concepts in Section 2.

@@

\section{Prerequisites}

>>>>

We further assume that the reader is familiar with the basic ideas and theory underlying Markov modeling and will only give a brief reminder of the basic concepts in Section~\ref{sec:prereq}.

@@

\section{Prerequisites}
\label{sec:prereq}
